Proportional multi-state multiple-cohort life table model

### 2018-05-02 MSLT/MSLTdoc.Rmd
Included age and sex cohort graphs in pdf

                      #                 paste0(if(disease == "ihd") {
                      # disease == "Ischemic heart disease"
                      # } else {
                      # if (disease == "istroke") {
                      # disease == "Ischemic stroke"
                      # } else {
                      # if (disease == "colon_cancer") {
                      # disease == "Colon cancer"
                      # } else {
                      # if (disease == "diabetes") {
                      # disease == "Diabetes"
                      # } else {
                      # if (disease == "breast_cancer") {
                      # disease == "Breast Cancer"}}}}}))

@@

                pdf(paste0(output_dir, "/", paste(age, sex, outcome, sep="_"), ".pdf"))
                grid_arrange_shared_legend (p1, p2, p3, p4, ncol = 2, nrow = 2, mainTitle = paste(ifelse(outcome == "mx", "Deaths", "Incidence"), sex, "cohort mid age", age),
                                          mainLeft = 'Cases', mainBottom = 'Age')
                dev.off()

@@

                pdf(paste0(output_dir, "/", paste(age, sex, outcome, sep="_"), ".pdf"))
                grid_arrange_shared_legend (p1, p2, p3, p4, p5, ncol = 2, nrow = 3, mainTitle = paste(ifelse(outcome == "mx", "Deaths", "Incidence"), sex, "cohort mid age", age), mainLeft = 'Cases', mainBottom = 'Age')
                dev.off()

@@

## Insert the plots in the rmarkdown doc

@@

>>>>

@@

                jpeg(paste0(output_dir, "/", paste(age, sex, outcome, sep="_"), ".jpeg"))
                grid_arrange_shared_legend (p1, p2, p3, p4, ncol = 2, nrow = 2, mainTitle = paste(ifelse(outcome == "mx", "Deaths", "Incidence"), sex, "cohort mid age", age),
                                          mainLeft = 'Cases', mainBottom = 'Age')
                dev.off()

@@

               jpeg(paste0(output_dir, "/", paste(age, sex, outcome, sep="_"), ".jpeg"))
                grid_arrange_shared_legend (p1, p2, p3, p4, p5, ncol = 2, nrow = 3, mainTitle = paste(ifelse(outcome == "mx", "Deaths", "Incidence"), sex, "cohort mid age", age), mainLeft = 'Cases', mainBottom = 'Age')
                dev.off()

@@

@@

```{r echo=FALSE, out.width='100%'}
## Loop to include graphs in the document
graphs_doc <- list()
index <- 1
for (age in i_age_cohort) {
      for (sex in i_sex)  {
        for (outcome in i_outcome) {

graphs_doc [[index]] <- c(paste("graphs/",age,"_",sex,"_", outcome,".jpeg", sep = ""))
          knitr::include_graphics(graphs_doc [[index]])
          index <- index + 1
        }
    }
}
 knitr::include_graphics(graphs_doc[c(1:64)])
```
